Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2022-12-05 R/model_fcs_check.Rmd
fcs comparison botanist_year vs botanist_year_exposition

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
    df_print: tibble
---

>>>>

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
---
